results notes

### 2022-09-01 RR_manuscript/results_notes.Rmd
added team descriptives from initial sign ups

# number of teams (initially)
no_teams_init <- readr::read_csv(
  here::here("data", "questionnaires", "msa_intake_form.csv")) %>% 
  select(Q6) %>% # Questions asking for team leader
  filter(!(row_number() %in% c(1, 2))) %>% 
  distinct() %>% 
  nrow

@@

`r no_teams_init %>% xfun::numbers_to_words() %>% stringr::str_to_title()` teams initially signed up to participate. 
`r (no_teams_init - no_teams) %>% xfun::numbers_to_words() %>% stringr::str_to_title()` of the proposed teams dropped out of the project during the analysis phase^[ADD REASONS]. 
The remaining `r no_teams` teams submitted their analysis in time and were coded by the three initiating authors (SC, JC, TR).

<!-- TR: not just 30 right? Please add the accurate info here -->

>>>>

# Get DF of all members with leader names
#
# NOTE: This can be simplified using 03_analyses_coding.Rmd
# I'll come back to this later and rewrite
#
team_leaders <- readr::read_csv(
  here::here("data", "questionnaires", "msa_intake_form.csv")) %>% 
  select(ResponseId, Q6) %>% # Questions asking for team leader
  filter(!(row_number() %in% c(1, 2))) %>% 
  mutate(leader = Q6, 
    leader = case_when(
    Q6 %in% c("Ali A-Hoorie", "Ali Al-Hoorie", "Ali H. Al-Hoorie") ~ "Ali Al-Hoorie", 
    Q6 %in% c("Alicea Megan Brown", "Alicia Brown") ~ "Alicia Brown", 
    Q6 %in% c("Dr Rory Turnbull", "Rory Turnbull") ~ "Rory Turnbull", 
    Q6 %in% c("Dr. Reenu Punnoose", "Reenu Punnoose") ~ "Reenu Punnoose", 
    Q6 %in% c("Dušan Nickolić", "Dušan Nikolić", "Dusan Nikolic", "Dusan Nikolic (dusan.nikolic1@ucalgary.ca)") ~ "Dusan Nikolic", 
    Q6 %in% c("Michael Gradoville (Arizona State Univ.)", "Michael Gradoville") ~ "Michael Gradoville", 
    Q6 %in% c("Nicole Rodriquez", "Nicole Rodriguez") ~ "Nicole Rodriguez", 
    Q6 %in% c("Scott James Perru", "Scott Perry") ~ "Scott James Perru", 
    Q6 %in% c("Tiphaine Caudrelier", "Tiphaine Cordelier") ~ "Tiphaine Caudrelier", 
    Q6 %in% c("University of Birmingham team under the team coordinator Zlatomira IIchovska", "Zlatomira IIchovska", "Zlatomira Ilchovska") ~ "Zlatomira Ilchovska", 
    Q6 %in% c("Vincent Hughes", "Vince Hughes") ~ "Vincent Hughes", 
    TRUE ~ leader
  )) %>% 
  select(ResponseId, leader)

# Team descriptives
#  - number of teams (initially)
#  - Avg size of each team
team_desc <- team_leaders %>% 
  group_by(leader) %>% 
  mutate(member_num = seq_along(ResponseId)) %>% 
  group_by(leader) %>% 
  mutate(n_members = max(member_num)) %>% 
  distinct(leader, n_members) %>% 
  ungroup() %>% 
  summarize(n_teams = nrow(.), 
            mean_size = mean(n_members), 
            sd_size = sd(n_members), 
            median_size = median(n_members))

# Need to join team leaders with msa_models$team to get the number of members on 
# each team (unless this data already lives somewhere else) 
# We could use : 
# https://docs.google.com/spreadsheets/d/1w39rU7O5ijzPmCpClVt5LEDIhzaLBDNrwfdMJUP86q8/edit#gid=0 
# But I'm thinking we need to make anonymous the team leader name info (offline) 
# for any of this to be a permanent solution.

@@

`r team_desc$n_teams %>% xfun::numbers_to_words() %>% stringr::str_to_title()` teams initially signed up to participate. 
`r (team_desc$n_teams - no_teams) %>% xfun::numbers_to_words() %>% stringr::str_to_title()` of the proposed teams dropped out of the project during the analysis phase^[ADD REASONS]. 
The remaining `r no_teams` teams submitted their analysis in time and were coded by the three initiating authors (SC, JC, TR).

<!-- TR: not just 30 right? Please add the accurate info here -->
<!-- 
JVC: I pulled the initial total from the uptake doc (see line 58-n) 
I think this is the most accurate count, by Stef might have another way
-->
